### 2025-01-24 scripts/compare-hard-shell-with-accessory.Rmd
deambiguate target DB
analysis of RM targets

```{r}
library(ggplot2)
```

@@

```{r}
wilcox.test(df_6_filter$discrepancy_selected, df_6_filter$discrepancy_others, paired = TRUE)

@@

>>>>

```{r}
library(ggplot2)
library(knitr)
library(xtable)
```

@@

```{r}
wilcox.test(df_4_filter$discrepancy_selected, df_4_filter$discrepancy_others, paired = TRUE)
wilcox.test(df_6_filter$discrepancy_selected, df_6_filter$discrepancy_others, paired = TRUE)

@@

```{r }
df_4 = read.csv('~/Downloads/trieste/test_4mer_targets.csv')
df_4_filter = df_4[df_4$PTU %in% ptu$PTU[ptu$pangenome.category=="include"],]
df_5 = read.csv('~/Downloads/trieste/test_5mer_targets.csv')
df_5_filter = df_5[df_5$PTU %in% ptu$PTU[ptu$pangenome.category=="include"],]
df_6 = read.csv('~/Downloads/trieste/test_6mer_targets.csv')
df_6_filter = df_6[df_6$PTU %in% ptu$PTU[ptu$pangenome.category=="include"],]

wilcox_tests = list(wilcox.test(df_4_filter$discrepancy_selected, df_4_filter$discrepancy_others, paired = TRUE),
                    wilcox.test(df_5_filter$discrepancy_selected, df_5_filter$discrepancy_others, paired = TRUE),
                    wilcox.test(df_6_filter$discrepancy_selected, df_6_filter$discrepancy_others, paired = TRUE))
results_df = data.frame(median_discrepancy_targets=c(median(df_4_filter$discrepancy_selected),
                                        median(df_5_filter$discrepancy_selected),
                                        median(df_6_filter$discrepancy_selected)),
           median_discrepancy_others=c(median(df_4_filter$discrepancy_others),
                                        median(df_5_filter$discrepancy_others),
                                        median(df_6_filter$discrepancy_others)),
           wilcoxon_stat=c(wilcox_tests[[1]]$statistic,
                           wilcox_tests[[2]]$statistic,
                           wilcox_tests[[3]]$statistic),
           p_value=c(wilcox_tests[[1]]$p.value,
                     wilcox_tests[[2]]$p.value,
                     wilcox_tests[[3]]$p.value))
kable(results_df, digits = 3, format = "html")

```

```{r}
# Read in results for RM targets
df_4 = read.csv('~/Downloads/trieste/test_RM_targets_k4.csv')
df_4_filter = df_4[df_4$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_4$discrepancy_selected!="None"],]
df_5 = read.csv('~/Downloads/trieste/test_RM_targets_k5.csv')
df_5_filter = df_5[df_5$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_5$discrepancy_selected!="None"],]
df_6 = read.csv('~/Downloads/trieste/test_RM_targets_k6.csv')
df_6_filter = df_6[df_6$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_6$discrepancy_selected!="None"],]

# Convert discrepancies to numeric (presence of None has messed this up)
df_4_filter$discrepancy_selected = as.numeric(df_4_filter$discrepancy_selected)
df_5_filter$discrepancy_selected = as.numeric(df_5_filter$discrepancy_selected)
df_6_filter$discrepancy_selected = as.numeric(df_6_filter$discrepancy_selected)

wilcox_tests = list(wilcox.test(df_4_filter$discrepancy_selected, df_4_filter$discrepancy_others, paired = TRUE),
                    wilcox.test(df_5_filter$discrepancy_selected, df_5_filter$discrepancy_others, paired = TRUE),
                    wilcox.test(df_6_filter$discrepancy_selected, df_6_filter$discrepancy_others, paired = TRUE))
results_df = data.frame(n_PTUs = c(nrow(df_4_filter),
                                   nrow(df_5_filter),
                                   nrow(df_6_filter)),
                        median_n_targets = c(median(df_4_filter$n_selected_kmers),
                                   median(df_5_filter$n_selected_kmers),
                                   median(df_6_filter$n_selected_kmers)),
  median_discrepancy_targets=c(median(df_4_filter$discrepancy_selected),
                                        median(df_5_filter$discrepancy_selected),
                                        median(df_6_filter$discrepancy_selected)),
           median_discrepancy_others=c(median(df_4_filter$discrepancy_others),
                                        median(df_5_filter$discrepancy_others),
                                        median(df_6_filter$discrepancy_others)),
           wilcoxon_stat=c(wilcox_tests[[1]]$statistic,
                           wilcox_tests[[2]]$statistic,
                           wilcox_tests[[3]]$statistic),
           p_value=c(wilcox_tests[[1]]$p.value,
                     wilcox_tests[[2]]$p.value,
                     wilcox_tests[[3]]$p.value))
kable(results_df, digits = 3, format = "html")
```
